Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-05 paper/ms.tex
updated until subsection 3.3 (models with highest nmock consistent with observations)

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}-f_{\rm occ}$ (right) planes for all models with
  $P>0.05$ in two different ways used to construct the mock
  surveys. The color code corresponds to the number of mock surveys
  that are found to be compatible with observations in terms of the KS
  test with $P>0.05$. Only regions of parameter space with at least
  one consistent mock survey are included. \label{fig:landscape}}   
\end{figure*}

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution.

The upper (lower) panels correspond to the {\texttt match} ({\texttt
  random}) method to build the mock surveys from individual
fields. The plot shows number of mock surveys consistent
with observations. There are between $550$ to $600$ models out of the
original $9000$ models that have at least one mock survey
consistent with observations.

In Figure \ref{fig:landscape} there are three regions of parameter
space that can be clearly distinguished. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of this models is compatible with observations as expected
from the results in the previous subsection. For these models the number
density of LAEs is too low compared to observations.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
the maximum mass $M_{\rm max}$ it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region in parameter space
one can thus find two extreme kinds of models.  One kind where the
mass interval is very narrow with sizes smaller than $<0.3$ dex (a
factor of two in mass) and others where the mass interval is 
extended (larger than $1.0$ dex) going up to the maximum halo mass
present in the simulation at that redshift (up to $2.5$ dex).

@@

Without any additional information our method allows us to infer that
most of the successful models are found in the second and third region of
parameter space where this result was already expected from halo
abundance calculations shown in Figure \ref{fig:halos}. In the next
section we reduce the size of this region by imposing tighter
constraints on the KS tests and consistency with the angular
correlation function.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a minimum number of mock survey
  realizations that are consistent with observations.
  \label{fig:high_success_rate}.}  
\end{figure*}

\subsection{Models with the highest success rates}

For each model ${\mathcal M}$ there are 15 different mock surveys. In the
previous section we presented the models that had at least one
mock survey with $P>0.05$.

Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
{\texttt  match} and {\texttt random} methods.  This shows that there
are between $80$ to $100$ models with all the 15 realizations with
$P>0.05$. Selection of these models as successful represents a
reduction of a factor of $\sim 6$ with respect to the total number of
mocks with at least one consistent mock.

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$. The results are very similar between the {\texttt
  match} and {\texttt random} methods. With this constraints the
number of consistent models with  $\log_{10}M_{\rm min}< 11.5$ are
greatly reduced. This corresponds to the regions in the parameter
space in Figure \ref{fig:landscape} that already had a low number of
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} one can see that there is not a
strong constraint on the occupation fraction $f_{\rm occ}$.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
%\hspace{5mm}
%\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}-f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of  mock surveys
  compatible with observations. Only regions of parameter  space with
  at least one consistent mock survey are  included. \label{fig:landscape}}     
\end{figure*}

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution. In total, there are between $550$ to $600$ models out of
the original $9000$ models that have at least one mock survey
consistent with observations.

In Figure \ref{fig:landscape} there are three regions of parameter
space that can be clearly distinguished. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of these models is compatible with observations as expected
from the arguments presented in the previous subsection. For these
models the number density of LAEs is too low compared to observations.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where, regardless of the value of
the maximum mass $M_{\rm max}$, it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region of parameter space
one can tfind two extreme kinds of models.  One kind where the
mass interval $\Delta M\equiv \log_{10} M_{\rm max} - \log_{10}M_{\rm
  min}$ is narrow with $\Delta M<1.0$ dex, others where the mass interval is 
extended $\Delta M>1.0$dex going up to the maximum halo mass
present in the simulation at that redshift, up to $\Delta M = 2.5$ dex
in some cases.

@@

Without any additional information our method allows us to infer that
most of the successful models are found in the second and third regions of
parameter space. This result was already expected from halo
abundance calculations shown in Figure \ref{fig:halos} and discussed
in the previous subsection.

However, the additional information we gain with this test is the
relative abundance of models in the parameter space. Not all the
models in the second region have an equal abundance. By inspection of
Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}<0.3$
are preferred.  In the next sub-section we explore in detail the
models in this region, imposing tighter constraints on the KS test
results and exploring the mocks' consistency with the angular correlation
function.

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
  consistent with the observed surface number density
  distribution in terms of the KS-test values $P>0.05$. Only $\sim
  100$ models have all their mocks consistent with observations. 
  \label{fig:high_success_rate}.}  
\end{figure}

\subsection{Models with the largest number of consistent mock surveys}

For each model ${\mathcal M}$ there are 15 different mock surveys. In the
previous section we presented the models that had at least one
mock survey with $P>0.05$. Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
{\texttt  match} and {\texttt random} methods.  This shows that there
are $\sim 100$ models with all the 15 mock survey realizations with
$P>0.05$.

We discard the models that have 14 mocks or less consistent with observations.
This cut represents a reduction by a factor of $\sim 6$ with respect
to the total number of models with at least one (1) consistent mock.

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$. With this constraints the
number of consistent models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are
greatly reduced. This corresponds to the regions in the parameter
space in Figure \ref{fig:landscape} that already had a low number of
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} one can see that there is not a
strong reduction on the favored values for the occupation fraction
$f_{\rm occ}$.
